### 2022-10-30 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (chapter5): Review Done

      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the heuristic pool size $K$ and maximum number of instances $I$.
      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a Binomial distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
\end{itemize}

@@

Finally, the event $C$ is a binomial distribution with parameter $\psi$. It is known that the conjugate prior to a binomial distribution is a Beta probability distribution (see Chapter \ref{chap:probability}). The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.

>>>>

      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the heuristic pool size $K$ and maximum number of instances $I$.
      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a\index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
\end{itemize}

@@

Finally, the event $C$ is a\index{Binomial probability distribution}Binomial probability distribution with parameter $\psi$. It is known that the conjugate prior to a\index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution (see Chapter \ref{chap:probability}). The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.

### 2022-10-30 dissertation/chapters/09-conclusion.tex
✨ (chapter5): Review Done

Credit assignment in the context of this dissertation was has 2 outcomes, true and false. Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution. Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic. Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution. Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version. A suggestion then is to learn which credit assignment to select. The results of this have show that credit assignment is problem-dependent. Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}. One could then include multiple strategies, each with varying exploration-exploitation trade-off.

>>>>

Credit assignment in the context of this dissertation was has 2 outcomes, true and false. Therefore, credit assignment and by definition performance evaluation is modeled as a \index{Binomial probability distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution. Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic. Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution. Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-Binomial probability distributions, it show be possible to extend credit assignment to a multivariate version. A suggestion then is to learn which credit assignment to select. The results of this have show that credit assignment is problem-dependent. Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}. One could then include multiple strategies, each with varying exploration-exploitation trade-off.
